\newpage
\section{Scenarios}  
The use cases discussed in the previous section will be worked out into scenarios filled with example data or package information.


\subsection{Packages}
Scenarios related to the packages themselves will be found here.

\input{scenarios/install-package-scenario.tex}
\input{scenarios/install-package-extended-scenario.tex}
\input{scenarios/reinstall-package-scenario.tex}
\input{scenarios/reinstall-package-extended-scenario.tex}
\input{scenarios/remove-package-scenario.tex}
\input{scenarios/downgrade-package-scenario.tex}
\input{scenarios/freeze-package-scenario.tex}


\subsection{Queries}
All query related scenarios will be found here.

\input{scenarios/show-package-details-scenario.tex}
\input{scenarios/show-installed-packages-scenario.tex}
\input{scenarios/show-package-install-scenario.tex}
\input{scenarios/show-package-build-scenario.tex}
\input{scenarios/show-frozen-packages-scenario.tex}
\input{scenarios/show-package-depends-scenario.tex}
\input{scenarios/show-untracked-files-scenario.tex}
\input{scenarios/show-journal-scenario.tex}
\input{scenarios/show-file-owner-scenario.tex}
\input{scenarios/search-package-descriptions-scenario.tex}
\input{scenarios/show-install-queue-scenario.tex}
\input{scenarios/show-available-patches-scenario.tex}


\subsection{Generation}
These scenarios relate to the generation of package information.

\input{scenarios/list-package-updates-scenario.tex}
\input{scenarios/HTML-package-listing-scenario.tex}


\subsection{Downloads}
Here you find the scenarios related to downloading packages, updates and news.

\input{scenarios/pull-package-sources-scenario.tex}
\input{scenarios/pull-package-tree-scenario.tex}
\input{scenarios/pull-news-feed-scenario.tex}


\subsection{Logging}
All logging scenarios will be presented here.

TODO: 5 scenarios
%\input{scenarios/log-package-install-scenario.tex}
%\input{scenarios/log-package-files-integrity-scenario.tex}
%\input{scenarios/log-package-build-scenario.tex}
%\input{scenarios/log-journal-scenario.tex}
%\input{scenarios/log-package-cache-scenario.tex}


\subsection{Fixing}
Scenarios dealing with fixing package problems are detailed here.

TODO: 7 scenarios
%\input{scenarios/purge-old-package-sources-scenario.tex}
%\input{scenarios/purge-old-logs-scenario.tex}
%\input{scenarios/verify-installed-package-files-scenario.tex}
%\input{scenarios/verify-installed-package-symlinks-scenario.tex}
%\input{scenarios/verify-installed-package-deps-scenario.tex}
%\input{scenarios/verify-installed-package-integrity-scenario.tex}
%\input{scenarios/fix-package-scenario.tex}


\subsection{Patching}
Scenarios dealing with patching both packages and package trees are presented here.

\input{scenarios/patch-package-update-scenario.tex}
\input{scenarios/patch-package-tree-update-scenario.tex}


\subsection{Maintaining}
Several maintenance scenarios are presented here.

\input{scenarios/central-build-scenario.tex}
\input{scenarios/source-location-package-tree-scenario.tex}


