\documentclass[a4paper]{article} 
\usepackage{abt}

\begin{document}

\title{ABout Time Linux - Eric's dep engine notes}

\author{%
    \begin{tabular}{cccc}
        \begin{tabular}{c}
            \small{Eric D. Schabell} \\ \scriptsize{erics@abtlinux.org}
        \end{tabular}
    \end{tabular}
}

\maketitle


\section{Introduction}
A few things they need to do:

\begin{enumerate}
  \item get to know abtlinux.org and wiki.abtlinux.org.
  \item become members.
  \item obtain email address for abtlinux.org, mail me!
  \item use forum topic for questions, comments.
  \item irc on freenode.net for comments (low, erics).
  \item in english, use latex, see template for doc, cases en scenarios.
\end{enumerate}

A few requirements I have:

\begin{itemize}

  \item dependency will specify a version (or use default?)
  \item dependencies will be ordered for a correct build process (dep engine!)
  \item support build-time and run-time dependencies:

  \begin{itemize}
    \item a buildDep is a dependency needed to build some package.
    \item RELIES ON (RO) - 'A' RO 'B'; then 'A' will be rebuilt if 'B' config changes.
    \item DEPENDS ON (DO) - 'A' DO 'B'; then 'A' will be rebuilt anytime 'B' is rebuilt.
    \item leads to several types of depends:

    \begin{itemize}
      \item permanently relies on
      \item permanently depends on
      \item optionally relies on
      \item optionally depends on
    \end{itemize}

  \end{itemize}

  \item prevent removal of packages with DEPENDS ON (DO) dependencies.
  \item auto add packages with RELIES ON (RO) dependencies to build queue if user rebuilds a package that relies on it.
  \item check for possible dependency breakage for a package, both up and down the dependency tree.
  \item generate the dependency tree for given package, both up and down.
  \item provide count of packages dependent on a given package.
  \item provide count of packages a given package is dependent on.
  \item provide list of packages installed w/o any depencencies.
  \item log dependency engine actions.

\end{itemize}

\end{document}
