\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Upgrade Configuration} \\
\hline
\textbf{Authors:} & RuDev \\
\hline
\textbf{Dates:} & 04-12-2006 \\
\hline
\textbf{Iteration:} & Focused \\
\hline
\textbf{Description:} & Upgrade the current configuration to the new standard \\
\hline
\textbf{Actors:} & AbT \\
\hline
\textbf{Preconditions:} & a. configManager has access to the package new configuration file(s). \newline b. configManager has generatad a list of all configuration files \\
\hline
\textbf{Triggers:} & AbT submits a requests to upgrade the current configuration with a new one from the package. \\
\hline
\textbf{Basic Course of Events:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{enumerate}
   \item AbT submits a requests to upgrade the current configuration with a new one from the package.
   \item Open list of all configfiles.
   \item Search in the list for the path of the current version of the configuration.
   \item Open the current configuration from the path given at step 3
   \item Compare the configuration variables from the current file given at step 4 with the variables from the new configuration file
   \item Backup the current configuration
   \item Return to AbT a request for updating the configuration with the differences found at step 5
   \item Return to AbT a request for updating version number.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Alternative Path:} & At Step 5: The configurations are equal \newline a. Skip steps 6,7,8  \\
\hline
\textbf{Exceptions:} & Current configuration could not be found \newline a. Return ERROR \newline\newline List of Configuration could not be opened \newline b. Return ERROR\\
\hline
\end{tabularx}
\newpage
\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Assumptions:} & \begin{enumerate} 
							\item AbT logs every action.
							\item The package for the upgrade process contains configuration file(s)
							\item configManager has access to read configuration file(s)
						\end{enumerate} \\
\hline
\textbf{Postconditions:} & 
  \begin{minipage}{\linewidth}
  \vspace{0.05em}
  \begin{enumerate}
    \item Current configuration is upgraded with the variables from the upgrade package.
	\item The old configuration is backuped
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline
\textbf{Related business rules:} & - \\
\hline
\end{tabularx}


