\medskip

\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Reinstall package} \\
\hline
\textbf{Use Case Steps:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{itemize}
    \item User command \textbf{'abt reinstall fortune'}.
    \item User asked if reconfigure or to use cached version of fortune.
    \item Rebuild requested, \textbf{fortune} added to install queue.
    \item Dependencies for this package are checked.
    \item Missing dependencies are added to install queue (sorted before this package).
    \item Packages needing rebuild after this package rebuilt added to intstall queue (sorted after this package).
    \item Reconfigure requested:
    \begin{itemize}
      \item Retrieve and use previous configuration as default.
    \end{itemize}
    \item \emph{Details} section processed:
    \begin{enumerate}
      \item NAME = fortune
      \item VERSION = \url{mod-9708}
      \item SRCFILE = \url{fortune-mod-9708.tar.gz}
      \item SRCDIR = \url{/usr/src/fortune-mod-9708}
      \item SRCURL = \url{http://www.fortune.org/pub/fortune-mod-9708.tar.gz}
      \item INTEGRITY = c016e3549942cbb
      \item URL = \url{http://www.fortune.org}
      \item LICENSE = BSD
      \item DESCRIPTION = "Random quotations from a large database."
    \end{enumerate}
    \item \emph{Pre} section processed:
    \begin{enumerate}
      \item Download package sources from \textbf{SRCURL}.
      \item Unpack package sources in \textbf{SRCDIR}.
      \item Reconfigure requested, query user to allow for configuration changes.
    \end{enumerate}
    \item \emph{Configure} section of package is processed.
    \begin{enumerate}
      \item Default used, sets install location to \textbf{\url{/usr/local}}.
      \item Run \textbf{configuration}.
    \end{enumerate}
  \end{itemize}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\end{tabularx}

\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Steps:} & 
\begin{minipage}{\linewidth}
  \vspace{0.05em}
  \begin{itemize}
    \item Save \url{/var/state/abt/install/fortune/fortune_mod-9708.config}.
    \item \emph{Build} section processed:
    \begin{enumerate}
      \item Default used, run \textbf{make}.
    \end{enumerate}
    \item Save \url{/var/state/abt/install/fortune/fortune_mod-9708.build}.
    \item \emph{Preinstall} section processed:
    \begin{enumerate}
      \item Default used, nothing done.
    \end{enumerate}
    item \emph{Install} section processed:
    \begin{enumerate}
      \item Default used, run \textbf{make install}.
    \end{enumerate}
    \item Save \url{/var/state/abt/install/fortune_mod-9708.install}.
    \item Save installed files integrity check \url{/var/state/abt/install/fortune_mod-9708.integrity}.
    \item \emph{Post} section processed:
    \begin{enumerate}
      \item Check which shells are installed.
      \item Add fortune message to these shell configurations.
    \end{enumerate}
    \item Package sources (build directories) are cleaned up (removed).
    \item Package is removed from install queue.
    \item Dependencies on this package are checked.
    \item User is notified that package was successfully installed.
  \end{itemize}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Alternative Path:} &
\begin{minipage}{\linewidth}
  \vspace{0.05em} 
  \begin{enumerate}
    \item Installing package that has been previously built (cached).
  \end{enumerate}
  \vspace{0.05em} 
\end{minipage}
\\
\hline
\end{tabularx}

\newpage


