\medskip

\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Install package} \\
\hline
\textbf{Use Case Steps:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{itemize}
    \item User command \textbf{'abt install fortune'}.
    \item \textbf{fortune} added to install queue.
    \item \emph{Details} section processed:
    \begin{enumerate}
      \item NAME = fortune
      \item VERSION = \url{mod-9708}
      \item SRCFILE = \url{fortune-mod-9708.tar.gz}
      \item SRCDIR = \url{/usr/src/fortune-mod-9708}
      \item SRCURL = \url{http://www.fortune.org/pub/fortune-mod-9708.tar.gz}
      \item MD5 = c016e3549942cbb8e86a3a343f865504
      \item URL = \url{http://www.fortune.org}
      \item LICENSE = BSD
      \item DESCRIPTION = "Random quotations from a large database."
    \end{enumerate}
    \item \emph{Pre} section processed:
    \begin{enumerate}
      \item Download package sources from \textbf{SRCURL}.
      \item Unpack package sources in \textbf{SRCDIR}.
    \end{enumerate}
    \item \emph{Configure} section of package is processed.
    \begin{enumerate}
      \item Default used, sets install location to \textbf{\url{/usr/local}}.
      \item Run \textbf{configuration}.
    \end{enumerate}
    \item Save \url{/var/state/abt/install/fortune/fortune_mod-9708.config}.
    \item \emph{Build} section processed:
    \begin{enumerate}
      \item Default used, run \textbf{make}.
    \end{enumerate}
    \item Save \url{/var/state/abt/install/fortune/fortune_mod-9708.build}.
  \end{itemize}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\end{tabularx}

\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Steps:} & 
\begin{minipage}{\linewidth}
  \vspace{0.05em}
  \begin{itemize}
    \item \emph{Preinstall} section processed:
    \begin{enumerate}
      \item Default used, nothing done.
    \end{enumerate}
    item \emph{Install} section processed:
    \begin{enumerate}
      \item Default used, run \textbf{make install}.
    \end{enumerate}
    \item Save \url{/var/state/abt/install/fortune_mod-9708.install}.
    \item Save installed files integrity check \url{/var/tmp/abt/install/fortune_mod-9708.integrity}.
    \item \emph{Post} section processed:
    \begin{enumerate}
      \item Default used, nothing done.
    \end{enumerate}
    \item Package configure file is added to \url{/var/log/abt/configure/}.
    \item Package build file is added to \url{/var/log/abt/build/}.
    \item Package install file is added to \url{/var/log/abt/install/}.
    \item Package integrity file is added to \url{/var/log/abt/integrity/}.
    \item Package sources (build directories) are cleaned up (removed).
    \item Package is removed from install queue.
    \item User is notified that package was successfully installed.
  \end{itemize}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Alternative Path:} &
\begin{minipage}{\linewidth}
  \vspace{0.05em} 
  \begin{enumerate}
    \item Installing package that has been previously built (cached).
  \end{enumerate}
  \vspace{0.05em} 
\end{minipage}
\\
\hline
\end{tabularx}

\newpage


