\medskip

\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Remove package} \\
\hline
\textbf{Use Case Steps:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{itemize}
    \item User command \textbf{'abt remove fortune'}.
    \item \textbf{fortune} added to remove queue.
    \item \emph{Details} section processed:
    \begin{enumerate}
      \item NAME = fortune
      \item VERSION = \url{mod-9708}
      \item SRCFILE = \url{fortune-mod-9708.tar.gz}
      \item SRCDIR = \url{/usr/src/fortune-mod-9708}
      \item SRCURL = \url{http://www.fortune.org/pub/fortune-mod-9708.tar.gz}
      \item INTEGRITY = c016e3549942cbb
      \item URL = \url{http://www.fortune.org}
      \item LICENSE = BSD
      \item DESCRIPTION = "Random quotations from a large database."
    \end{enumerate}
    \item Check to ensure package installed.
    \item Dependencies for this package are checked.
    \item Eventual broken dependencies are added to install queue to be rebuilt.
    \item Retrieve fortune logs: \url{/var/log/abt/*/fortune-mod-9708/*}.
    \begin{enumerate}
      \item Package configure file: \url{/var/log/abt/configure/}.
      \item Package build file: \url{/var/log/abt/build/}.
      \item Package install file: \url{/var/log/abt/install/}.
      \item Package integrity file: \url{/var/log/abt/integrity/}.
      \item Package sources: \url{/var/spool/abt/fortune-mod-9708.tar.gz}
    \end{enumerate}
    \item \emph{Preremove} section processed:
    \begin{enumerate}
      \item Process any given special instructions found here.
    \end{enumerate}
  \end{itemize}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\end{tabularx}

\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Steps:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{itemize}
    \item Files cached in \url{/var/state/abt/cached/fortune/*}.
    \item Process any configuration files:
    \begin{enumerate}
      \item Cache copies of existing configuration files: \url{fortune_mod-9708.user-configs}.
      \item Base removal/keeping of existing configuration files on user provided option (globally set).
    \end{enumerate}
    \item Create compressed tarball of all relevant logs.
    \item Remove fortune installed files.
    \item User notified that fortune-mod-9708 has been successfully removed.
  \end{itemize}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Alternative Path:} & None. \\
\hline
\end{tabularx}

\newpage


