
\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Install package} \\
\hline
\textbf{Description:} & 
The basic steps to be taken to install a software package. \\
\hline
\textbf{Actors:} & User \\
\hline
\textbf{Preconditions:} & Package description is available. \\
\hline
\textbf{Triggers:} & abt install $<$pkg$>$ \\
\hline
\textbf{Basic Course of Events:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{enumerate}
    \item User submits an install package request.
    \item Package to be installed is placed in install queue.
    \item Dependencies for this package are checked.
    \item \emph{Details} section of package is processed.
    \item \emph{Pre} section of package is processed.
    \item \emph{Configure} section of package is processed.
    \item Copy of configuration is saved.
    \item \emph{Build} section of package is processed.
    \item Copy of build is saved.
    \item \emph{Preinstall} section of package is processed.
    \item \emph{Install} section of package is processed.
    \item A list of installed files is saved.
    \item An integrity check is created on each installed file and saved.
    \item \emph{Post} section of package is processed.
    \item Package is added to installed packages list.
    \item Package is removed from install queue.
    \item Package build is cached for future usage.
    \item Package sources (build directories) are cleaned up (removed).
    \item User is notified that package was successfully installed.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline
\end{tabularx}

\newpage
\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Exceptions:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{enumerate}
    \item The package is already installed, report this and terminate with success.
    \item The \emph{details/pre/prebuild/preinstall/post} sections fail, report error and process stops.
    \item \emph{Configure} section fails, report error, save copy of configuration and process stops.
    \item \emph{Build} section fails, report error, save copy of build log and process stops.
    \item \emph{Install} section fails, report error, clean up any installed files (all or nothing is installed) and process stops.
    \item Dependency breakage detected, add broken package to install queue.
    \item Existing configuration files detected during installation of new files, query user to either; backup old versions and replace with new, keep old in place and copy new one next to it, replace old with new, default to the first choice.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Postconditions:} &
\begin{minipage}{\linewidth}
  \vspace{0.05em}
  \begin{enumerate}
    \item Package is installed.
    \item For existing packages, when error is reported, then package is still in install queue.
    \item For broken dependencies, package added to install queue.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline
\end{tabularx}


