
\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Remove package} \\
\hline
\textbf{Description:} & 
Remove an installed package. \\
\hline
\textbf{Actors:} & User \\
\hline
\textbf{Preconditions:} & 
Requested package is installed. \\
\hline
\textbf{Triggers:} & abt remove $<$pkg$>$ \\
\hline
\textbf{Basic Course of Events:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{enumerate}
    \item User submits a remove package request.
    \item Check for dependency breakage, report for user input.
    \item Package is added to uninstall queue.
    \item Tarball is created containing the following:
    \begin{enumerate}
      \item Copy of installed configuration files.
      \item Copy of configuration.
      \item Copy of build.
      \item List of installed files.
      \item List of integrity checks for installed files.
      \item Copy of installed files.
      \item Copy of source files for this version.
      \item Copy of package data (detail, pre, configure, etc).
    \end{enumerate}
    \item Installed package files are removed.
    \item Package is removed from installed packages list.
    \item Package is removed from uninstall queue.
    \item Check for dependency breakage.
    \item User is notified that package was successfully uninstalled.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Exceptions:} & 
If package not installed, exit with success.
\\
\hline 
\textbf{Postconditions:} &
\begin{minipage}{\linewidth}
  \vspace{0.05em}
  \begin{enumerate}
    \item The package is no longer installed.
    \item There is a tarball containing everything needed to re-create the package that was just removed.
    \item For broken dependencies, package added to install or uninstall queues.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline
\end{tabularx}

