
\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Fix package} \\
\hline
\textbf{Description:} & 
Check the package for missing/broken libraries, symlinks and file permissions.
\\
\hline
\textbf{Actors:} & User \\
\hline
\textbf{Preconditions:} & Package to be fixed is installed. \\
\hline
\textbf{Triggers:} & abt fix $[$pkg$]$ \\
\hline
\textbf{Basic Course of Events:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{enumerate}
    \item User submits a fix request, either on a package or on entire installed packages list if no package is given.
    \item Package(s) are checked by comparing:
    \begin{enumerate}
      \item Installed files are checked if they exist.
      \item Installed files are checked for integrity.
      \item Installed libraries are checked for dependency breakage.
      \item Configuration files are checked only for existence.
    \end{enumerate}
    \item Any problems found result in User being asked if rebuild wanted.
    \item Default if User does not respond is to rebuild package.
    \item Check for possible dependency breakage.
    \item After package(s) checked, overview of good, bad and fixed package(s) reported to User.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Exceptions:} & 
Any problems results in package(s) being left in the install or uninstall queues. 
\\
\hline 
\textbf{Postconditions:} &
\begin{minipage}{\linewidth}
  \vspace{0.05em}
  \begin{enumerate}
    \item User has report of good, bad and fixed package(s).
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline
\end{tabularx}


