\begin{tabularx}{\linewidth}{|l|X|}
\hline
\textbf{Use Case Name:} & \textbf{Look for dependencies up the tree} \\
\hline
\textbf{Authors:} & AbTCans\\
\hline
\textbf{Dates:} & 13-12-2005\\
\hline
\textbf{Iteration:} & Focused\\
\hline
\textbf{Description:} & Look for packages up the tree, i.e. packages depending on the given package.\\
\hline
\textbf{Actors:} & abt \\ 
\hline
\textbf{Preconditions:} & Dependency engine has access to the package dependency description.\\
\hline
\textbf{Triggers:} & Triggering these actions in case of all operations, except for Install.\\
\hline
\textbf{Basic Course of Events:} & 
\begin{minipage}{\linewidth} 
  \vspace{0.05em}
  \begin{enumerate}
   \item Abt submits a request for a list of dependencies up the tree from a given package (and a depth).
   \item Look for packages up the tree (to a given depth).
   \item Generate a list dependencies down the tree.
   \item Apply tree-algorithm (see Appendix) to fill the list.
   \item Return the list of dependencies up the tree.
   \item Write actions to the log.
  \end{enumerate}
  \vspace{0.05em}
\end{minipage}
\\
\hline 
\textbf{Alternative Path:} & In step 2, if no dependencies are found, an empty list is returned.\\
\hline
\textbf{Exception Paths:} & If dependency data can not be retrieved from a package, return ERROR. \\
\hline
\textbf{Assumptions:} & Abt has a log to write actions to. \\
\hline

\textbf{Postconditions:} & Generated list of dependencies up the tree.\\
\hline
\textbf{Related business rules:} & None\\
\hline
\end{tabularx}


  